Competition

### 2020-09-16 R/competition wrangling.Rmd
corrected density at closest distance by subtracting shoots of focal plant.

I want to use the `row` and `colunn` to figure out how many neighbors each plant has. I should exclude plants on edges, because I don't know about their neighbors outside of the plot.

@@

```{r}
#density between 5m and 15m away
dist_5_15 <-
  dist_full %>% 
  filter(dist >=5, dist <15) %>% 
  group_by(row_from, column_from) %>% 
  summarize(n_neighbors_5_15 = sum(n_plants, na.rm = TRUE),
            n_cells = n(),
            density_5_15 = n_neighbors_5_15/n_cells,
            shtsper_5_15 = sum(n_shts, na.rm = TRUE)/n())
```
So at [1,1] there are only 3 cells between 5 and 15m away, there are a total of 6 plants in those cells, so the conspecific density at that distance is 2.0 plants / 100m^2 or 3.66 shoots / 100m^2

@@

```{r}
full_test <- full_join(ha_test, dist_5_15, by = c("row_number" = "row_from", "column" = "column_from"))
head(full_test)
```

@@

```{r}
dens_0_10 <-
  ha_dist %>% 
  filter(dist>0 & dist <=10) %>% 
  group_by(plot, year, row_from, column_from) %>% 
  summarize(density_0_10 = sum(n_shts, na.rm = TRUE)/n())
left_join(ha, dens_0_10, by = c("plot", "year", "row_number" = "row_from", "column" = "column_from")) %>% 
  arrange(plot, year, row_number, column)
```

@@

```{r}
ha_new <- 
  left_join(ha, x,
          by = c("plot", "year", "row_number" = "row_from", "column" = "column_from")) %>% 
  arrange(plot, year, row_number, column)
ha_new
```

>>>>

I want to use the `row` and `colunn` to figure out how many neighbors each plant has. I should exclude plants on edges, because I don't know about their neighbors outside of the plot.
# TODO:

- density at distance 0 shouldn't include the focal plant

@@

```{r}
#density between 0m and 10m away
dist_0_10 <-
  dist_full %>% 
  filter(dist >=0, dist <10) %>% 
  group_by(row_from, column_from) %>% 
  summarize(n_neighbors_0_10 = sum(n_plants, na.rm = TRUE),
            n_cells = n(),
            density_0_10 = n_neighbors_0_10/n_cells,
            shtsper_0_10 = sum(n_shts, na.rm = TRUE)/n())
```
So at [1,1] there are only 3 cells between 5 and 15m away, there are a total of 6 plants in those cells, so the conspecific density at that distance is 2.0 plants / 100m^2 or 3.66 shoots / 100m^2

@@

```{r}
full_test <- full_join(ha_test, dist_0_10, by = c("row_number" = "row_from", "column" = "column_from"))
head(full_test)
```
For the nearest distances (0-10m), I need to subtract the number of shoots in the focal plant.

```{r}
full_test %>% 
  # mutate(shtsper_0_10 = shtsper_0_10 - shts) %>% 
  arrange(row, column)

full_test %>% 
  group_by(row, column) %>% 
  summarize(n = n(), n_shts = sum(shts))
```

@@

```{r}
dens_0_10 <-
  ha_dist %>% 
  filter(dist>=0 & dist <10) %>% 
  group_by(plot, year, row_from, column_from) %>% 
  summarize(density_0_10 = sum(n_shts, na.rm = TRUE)/n())
left_join(ha, dens_0_10, by = c("plot", "year", "row_number" = "row_from", "column" = "column_from")) %>% 
  arrange(plot, year, row_number, column)
```

@@

```{r}
ha_new <- 
  left_join(ha, x,
          by = c("plot", "year", "row_number" = "row_from", "column" = "column_from")) %>% 
  arrange(plot, year, row_number, column)
ha_new
```
Finally, I need to correct the closest density by subtracting shoots of the focal plant.

```{r}
ha_new <- ha_new %>% mutate(density_0_10 = density_0_10 - shts)
```
